\ttitle

### 2013-05-30 Chapters/Chapter2.tex
Add literature list to sections

%----------------------------------------------------------------------------------------
\section{Outline}
\begin{itemize}
  \item Literature review about Temporal Segmentation (previous draft was more about classification)
  \item Consider methods for the context of filter-methods for classification
  \item Take a loot at 3-4 different kind of methods for change detection:
    \begin{itemize}
      \item Dimensionality reduction
      \item Density-ratio estimation
      \item Support Vector Machines (?) - if there are more sources about this
      \item CUSUM - or other more traditional methods
    \end{itemize}
  \item With each method, shortly look at characteristics, strengths and weaknesses and consider applicability to accelerometer sensor data
\end{itemize}

\section{Statistical framework}
Many applications require the detection of time points at which underlying properties of a system change.
This problem thus has received a lot of attention in the fields of data mining, etc... *** list and refs ***.

Some methods, such as the CUSUM (cumulative sum) \cite{basseville1993detection} and GLR (generalized likelihood ratio) \cite{gustafsson1996marginalized, gustafsson2000adaptive} formulate this problem in the statistical framework in the following sense.
A time series is represented by an underlying probability distribution generating the data.
The PDFs (probability distribution function) of two consecutive segments around a target point are compared.
If they differ significantly, the target point is considered as a change point \cite{kawahara2009change}.

%----------------------------------------------------------------------------------------
\section{Change-detection by Dimensionality Reduction / Covariance structure}

%----------------------------------------------------------------------------------------
\input{./Chapters/Chapter2/density_ratio}

%----------------------------------------------------------------------------------------
\input{./Chapters/Chapter2/svm}

%----------------------------------------------------------------------------------------
\section{Change-detection by Cumulative Sum}

>>>>

%----------------------------------------------------------------------------------------
\section{Outline}
\begin{itemize}
  \item Literature review about Temporal Segmentation (previous draft was more about classification)
  \item Consider methods for the context of filter-methods for classification
  \item Take a loot at 3-4 different kind of methods for change detection:
    \begin{itemize}
      \item Introduction with a lot of techniques
      \item Explain why look at a few
      \item CUSUM - or other more traditional methods
      \item Density-ratio estimation
      \item Support Vector Machines (?) - if there are more sources about this
      \item (Dimensionality reduction)
    \end{itemize}
  \item With each method, shortly look at characteristics, strengths and weaknesses and consider applicability to accelerometer sensor data
\end{itemize}

% \section{Statistical framework}\label{statistical-framework}
% Many applications require the detection of time points at which the underlying properties of a system change.
% This problem thus has received a lot of attention in the fields of data mining, etc... *** list and refs ***.
% Often this problem is formulated in a statistical framework, by inspecting the data generating PDF (Probability Density Function) of the time series data.
% A change point is then defined as a significant change in the properties of the PDF, such as the mean and variance.

% The widely used CUSUM (cumulative sum) method by Basseville \etal \cite{basseville1993detection}, and the GLR (Generalized Likelihood Ratio) by Gustafsson \cite{gustafsson1996marginalized,gustafsson2000adaptive} take this approach.
% The former originates from control methods for detection from bench marks.
% The latter compares the logarithm of the likelihood ratio over two consecutive intervals.
% These two methods is discussed and analyzed in section \ref{cusum-glr}.

% The GLR method, as with others, relies on pre-specified parametric model assumptions and considers the data be independent over time, which makes it less flexible to real-world applications.
% The proposed methods by Kawahara \etal \cite{kawahara2009change} and Lui \etal \cite{liu2013change} try to overcome these problems by estimating the \emph{ratio} between the PDF, instead of estimating each PDF.
% This approach is discussed and analyzed in section \ref{density-ratio}.

% The density-estimation methods, as with the GLR, rely on the log-likelihood ratio between PDFs.
% The method of Camci \cite{camci2010change} takes an other approach within the statistical framework, by using a SVM (Support Vector Machine).
% One problem it tries to overcome is the (claimed) weakness of many methods to detect a decrease in variance.
% The method represents the distribution over the data points as a hyper-sphere in a higher dimension using kernel trick.
% A change in the PDF is represented by a change in the radius of this sphere.
% Section \ref{svm} discusses the SVM-method.

% The final method under consideration, change detection via (intrinsic) dimensionality reduction, takes a different point of view.
% Opposed to the other discussed methods, dimensionality reduction is framed in the MDL (Minimum Description Length) framework.
% It uses the estimated underlying number of parameters of the time series as a model for change detection.
% Section \ref{dim-reduction} discuses this method.

%----------------------------------------------------------------------------------------
% CUSUM and GLR
\input{./Chapters/Chapter2/cusum_glr}

%----------------------------------------------------------------------------------------
% Density Ratio Estimation
\input{./Chapters/Chapter2/density_ratio}

%----------------------------------------------------------------------------------------
% Support Vector Machines
\input{./Chapters/Chapter2/svm}

%----------------------------------------------------------------------------------------
% Dimensionality reduciton
\input{./Chapters/Chapter2/dim_reduction}

### 2013-05-30 Chapters/Chapter2/cusum_glr.tex
Add literature list to sections

>>>>

Papers:
\begin{itemize}
  \item Use of Cumulative Sums of Squares for Retrospective Detection of Changes of Variance, 1994, 162 refs \cite{inclan1994use} \\
  Implemented this algorithm.
  \item An adaptive CUSUM-based test for signal change detection, 2006, 15 refs. \cite{alippi2006adaptive}
  \item The MOSUM of squares test for monitoring variance changes \cite{hsu2007mosum}
\end{itemize}

### 2013-05-30 Chapters/Chapter2/density_ratio.tex
Add introduction Chapter 2
Add literature list to sections

% !TEX root = ../../main.tex
\section{Change-detection by Density-Ratio Estimation}

>>>>

% !TEX root = ../../main.tex
\section{Change-detection by Density-Ratio Estimation}\label{density-ratio}

Papers:
\begin{itemize}
  \item Change-Point Detection in Time-Series Data by Direct Density-Ratio Estimation, 2009, 45 refs \cite{kawahara2009change}
  \item Change-Point Detection in Time-Series Data by Relative Density-Ratio Estimation, 2013, 3 refs \cite{liu2013change}
  \item Density ratio estimation in machine learning (Book), 2009, 24 refs \cite{sugiyama2012density}
\end{itemize}
